### 2012-06-25 inst/examples/voi_May.Rmd
Queueing up May model with allee effect

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`

@@

# Calculating the value of information

@@

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

Chose the state equation / population dynamics function

``` {r }
f <- function(x,h,p){
  sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}
````

With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.

``` {r }
pars <- c(r, K)
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_May/", verbose=TRUE or`

@@

# Value of information under the May alternative stable states model with uniform noise

@@

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````
With parameters

``` {r pars}
pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
K <- 8 # approx
````

Ask R to show us how this function is defined, and plot the transition point using these parameters.

``` {r showMay, fig.keep="last"}
May
curve(.75*(1-x/10), 0, 10)
curve(1*x^2/(x^3+1), 0, 10, add=T, col="blue")
curve(1.9*x^2/(x^3+1), 0, 10, add=T, col="red")
````
